\LARGE \bf A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself

### 2014-11-27 rebuttal_sorted.txt

Again, we agree and will comply, and would like to thank the reviewer for their time in compiling this list.

>    - The authors appear to violate double-blindness in up to 3 ways: by
>    providing a URL to their code that contains “EPFL”, an apparent self
>    citation “Learning to write with a robot” from EPFL (given that this
>    paper claims to be the “first known robotic partner which children can
>    teach handwriting”, I assume that this citation is the same project),
>    and an apparent experimenter’s face appearing in Figure 8.

This was an oversight on our side and we apologise for letting it go undetected.

>    “a shape center of 0” - What’s really meant here is that the
>    normalized trajectory points average 0, correct? (If so, this quotation
>    is both vague and incorrect, since the trajectory and the shape it makes
>    are not the same thing.)
DONE
We can clarify that we indeed refer to a shape with its centre at the origin, not 0-average trajectory.

### 2014-11-27 main.tex
R1 shape centre clarification
R1 robot letter not in response to corrections

PCA has been performed on a set of letter paths captured from a digital pen,
using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
each letter (2 repetitions from 60 adult users). While it may be appropriate in future work to
identify the location of salient features of the shapes which are robust to unanticipated user input,
the features are currently taken as $n$ uniformly spaced points along the shape
path. The
points are arranged into an observation vector presented in (\ref{eq:obsVec}),
where $x_i$ and $y_i$ represent the coordinates of each of the points along the
path. The observation shapes are normalised such that they have a shape
centre of ${\bf 0}$ and a unit maximum dimension.

@@

    \textbf{The system has been validated as a technically sound
        autonomous interaction.} The interaction setup including the teachable
        robotic agent withstood the interaction for a total of 160 minutes, with
        the robot writing 335 letters, 152 of which in response to
        demonstrations received from the 21 children. During this time, technical 
	intervention was only required for the three instances that the robot fell 
	later in the day. Otherwise, the technical components of the system operated 
	autonomously and as expected over the sessions.
        %, with only verbal interaction for prompting being required from an observing researcher.

>>>>

PCA has been performed on a set of letter paths captured from a digital pen,
using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
each letter (2 repetitions from 60 adult users). While it may be appropriate in future work to
identify the location of salient features of the shapes which are robust to unanticipated user input,
the features are currently taken as $n$ uniformly spaced points along the shape
path. The
points are arranged into an observation vector presented in (\ref{eq:obsVec}),
where $x_i$ and $y_i$ represent the coordinates of each of the points along the
path. The observation shapes are normalised to have a unit maximum dimension 
and centre at the origin.

@@

    \textbf{The system has been validated as a technically sound
        autonomous interaction.} The interaction setup including the teachable
        robotic agent withstood the interaction for a total of 160 minutes. During this
        time the robot wrote 335 letters, 152 of which in response to
        demonstrations received from the 21 children and the remaining while writing 
        new words. During this time, technical 
	intervention was only required for the three instances that the robot fell 
	later in the day. Otherwise, the technical components of the system operated 
	autonomously and as expected over the sessions.
        %, with only verbal interaction for prompting being required from an observing researcher.
